Location of Bivalve Farms

### 2021-02-10 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished up making sure no bivalve points fall on land

coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
mapview(coast_raw)
```

@@

```{r}
world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
plot(world)

Guernsey <- ne_countries(scale = 10, country = "Guernsey", returnclass = "sf")

#info of our spatial vector object
Guernsey
mapview(Guernsey)
plot(Guernsey)

Guernsey_world_crs <- st_transform(Guernsey, crs(world))

Guernsey_world_crop <- st_crop(world, Guernsey_world_crs) %>%
  dplyr::filter(scalerank == 5) ## filter for the appropriate island
plot(Guernsey_world_crop)
mapview(Guernsey_world_crop)

Guernsey_crop <- as(Guernsey_world_crop, "Spatial")

@@

Guernsey_points <- st_as_sf(Guernsey_points_lines)
mapview(Guernsey_points)

@@

```{r}
world <- rnaturalearth::ne_coastline(scale = 10) #world map with 10m resolution
plot(world)

@@

#info of our spatial vector object
slovenia
mapview(slovenia)
plot(slovenia)

@@

slovenia_world_crs <- st_transform(slovenia, crs(world))

slovenia_world_crop <- st_crop(world, slovenia_world_crs) ## crop to slovenia extent
plot(slovenia_world_crop)
mapview(slovenia_world_crop)

slovenia_crop <- as(slovenia_world_crop, "Spatial")
plot(slovenia_crop)
mapview(slovenia_crop)

slovenia_points_lines <- sample.line(slovenia_crop, n = 86) ## equally place the number of farms along the coastline 
class(slovenia_points_lines)
plot(slovenia_points_lines)

slovenia_points <- st_as_sf(slovenia_points_lines)
mapview(slovenia_points)

## Now filter out the points that fall outside of Slovenia
slovenia_points_final <- slovenia_points[12:31,]
mapview(slovenia_points_final)

@@

croatia <- ne_countries(scale = 110, country = "Croatia", returnclass = "sf")

#info of our spatial vector object
croatia
mapview(croatia)
plot(croatia)

@@

croatia_world_crop <- st_crop(world, croatia_world_crs) ## crop to croatia extent
plot(croatia_world_crop)
mapview(croatia_world_crop)

croatia_crop <- as(croatia_world_crop, "Spatial")
plot(croatia_crop)
mapview(croatia_crop)

croatia_points_lines <- sample.line(croatia_crop, n = 340) ## equally place the number of farms along the coastline 
class(croatia_points_lines)
plot(croatia_points_lines)

croatia_points <- st_as_sf(croatia_points_lines)
mapview(croatia_points)

## Now filter out the points that fall outside of croatia: rows 57-70
croatia_points_final <- croatia_points[2:267,]
mapview(croatia_points_final)

@@

```{r}
world <- ne_coastline(scale = 10) #world map with 10m resolution
plot(world)

@@

#info of our spatial vector object
kerala_state
mapview(kerala_state)
plot(kerala_state)

kerala_state_world_crs <- st_transform(kerala_state, crs(world))

kerala_state_world_crop <- st_crop(world, kerala_state_world_crs) ## crop to kerala extent
plot(kerala_state_world_crop)
mapview(kerala_state_world_crop)

kerala_state_crop <- as(kerala_state_world_crop, "Spatial")
plot(kerala_state_crop)
mapview(kerala_state_crop)

kerala_state_points_lines <- sample.line(kerala_state_crop, n = 250) ## equally place the number of farms along the coastline 
class(kerala_state_points_lines)
plot(kerala_state_points_lines)

kerala_state_points <- st_as_sf(kerala_state_points_lines)
mapview(kerala_state_points)

## Now filter out the points that fall outside of kerala_state: rows 57-70
# kerala_state_points_final <- kerala_state_points[c(1:34,42:67), ]
# mapview(kerala_state_points_final)

## get lat lon
ind_pts <- st_centroid(kerala_state_points)

@@

@@

#info of our spatial vector object
north_korea
mapview(north_korea)
plot(north_korea)

north_korea_world_crs <- st_transform(north_korea, crs(world))

north_korea_world_crop <- st_crop(world, north_korea_world_crs) ## crop to north korea extent
plot(north_korea_world_crop)
mapview(north_korea_world_crop)

north_korea_crop <- as(north_korea_world_crop, "Spatial")
plot(north_korea_crop)
mapview(north_korea_crop)

north_korea_points_lines <- sample.line(north_korea_crop, n = 67) ## equally place the number of farms along the coastline 
class(north_korea_points_lines)
plot(north_korea_points_lines)

north_korea_points <- st_as_sf(north_korea_points_lines)
mapview(north_korea_points)

## Now filter out the points that fall outside of north_korea: rows 57-70
north_korea_points_final <- north_korea_points[c(1:34,42:67), ]
mapview(north_korea_points_final)

@@

world <- ne_coastline(scale = 110) #world map with 110m resolution
plot(world)

#info of our spatial vector object
sta_catarina
mapview(sta_catarina)
plot(sta_catarina)

sta_catarina_world_crs <- st_transform(sta_catarina, crs(world))

sta_catarina_world_crop <- st_crop(world, sta_catarina_world_crs) ## crop to santa catarina extent
plot(sta_catarina_world_crop)
mapview(sta_catarina_world_crop)

sta_catarina_crop <- as(sta_catarina_world_crop, "Spatial")
plot(sta_catarina_crop)
mapview(sta_catarina_crop)

sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 27) ## equally place the number of farms along the coastline 
class(sta_catarina_points_lines)
plot(sta_catarina_points_lines)

sta_catarina_points <- st_as_sf(sta_catarina_points_lines)
mapview(sta_catarina_points)

@@

world <- ne_coastline(scale = 50) #world map with 50m resolution
plot(world)

@@

capiz_world_crs <- st_transform(capiz, crs(world))

capiz_world_crop <- st_crop(world, capiz_world_crs) ## crop to extent
plot(capiz_world_crop)
mapview(capiz_world_crop)

capiz_crop <- as(capiz_world_crop, "Spatial")
plot(capiz_crop)
mapview(capiz_crop)

capiz_points_lines <- sample.line(capiz_crop, n = 300) ## equally place the number of farms along the coastline 
class(capiz_points_lines)
plot(capiz_points_lines)

capiz_points <- st_as_sf(capiz_points_lines)
mapview(capiz_points)

world <- ne_coastline(scale = 110) #world map with 110m resolution
plot(world)

# now do negros
negros <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Negros Occidental")
mapview(negros)
plot(negros)

negros_world_crs <- st_transform(negros, crs(world))

negros_world_crop <- st_crop(world, negros_world_crs)

negros_world_crop <- head(negros_world_crop, 1)
plot(negros_world_crop)
mapview(negros_world_crop)

negros_crop <- as(negros_world_crop, "Spatial")
plot(negros_crop)
mapview(negros_crop)

@@

world <- ne_coastline(scale = 110) #world map with 50m resolution
plot(world)

# now do samar 
samar <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Samar")
mapview(samar)
plot(samar)

samar_world_crs <- st_transform(samar, crs(world))

samar_world_crop <- st_crop(world, samar_world_crs)

samar_world_crop <- head(samar_world_crop, 1)
plot(samar_world_crop)
mapview(samar_world_crop)

samar_crop <- as(samar_world_crop, "Spatial")
plot(samar_crop)
mapview(samar_crop)

samar_points_lines <- sample.line(samar_crop, n = 250) ## equally place the number of farms along the coastline 
class(samar_points_lines)
plot(samar_points_lines)

samar_points <- st_as_sf(samar_points_lines)
mapview(samar_points)

>>>>

coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
# mapview(coast_raw)
```

@@

```{r}
## read in country shapefile
Guernsey <- ne_countries(scale = 10, country = "Guernsey", returnclass = "sf")

#info of our spatial vector object
mapview(Guernsey)
plot(Guernsey)

## transform to same crs at the coast file so we can crop
Guernsey_world_crs <- st_transform(Guernsey, crs(coast_raw))

# crop the to the coast file, and select the main island 
Guernsey_world_crop <- st_crop(coast_raw, Guernsey_world_crs) %>%
  dplyr::filter(FID %in% c(220920, 220921, 220922)) %>% ## filter for the appropriate island
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
  ungroup()

plot(Guernsey_world_crop)
mapview(Guernsey_world_crop)
class(Guernsey_world_crop)
crs(Guernsey_world_crop)

g_meters <- st_transform(Guernsey_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(g_meters)

buff <- st_buffer(g_meters, dist = 1000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

buffer_outline <- linestring[1,]  ## grab the outline row 
mapview(buffer_outline)

## now reproject back to original 
buffer_outline_fixed <- st_transform(buffer_outline, crs = crs(Guernsey_world_crop))

## make a spatiallinesdataframe so we can use sample.line
Guernsey_crop <- as(buffer_outline_fixed, "Spatial")
class(Guernsey_crop)
mapview(Guernsey_crop)

@@

Guernsey_points <- st_as_sf(Guernsey_points_lines)
mapview(Guernsey_points, color = "red") + mapview(Guernsey_world_crop)

st_distance(Guernsey_points, Guernsey_world_crop)
# Units: [m]
#          [,1]
# [1,] 992.6726
# [2,] 992.6273
# [3,] 992.6395
# [4,] 992.3816
# [5,] 992.3755
# [6,] 992.7368
# [7,] 992.6771
## close enough to 1 km

@@

```{r}
# world <- rnaturalearth::ne_coastline(scale = 10) #world map with 10m resolution
# plot(world)

@@

#info of our spatial vector object
mapview(slovenia)
plot(slovenia)

@@

slovenia_world_crs <- st_transform(slovenia, crs(coast_raw))

slovenia_world_crop <- st_crop(coast_raw, slovenia_world_crs) %>% ## crop to slovenia extent
  filter(FID %in% c(46261, 46262)) %>%
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
  ungroup()

plot(slovenia_world_crop)
mapview(slovenia_world_crop)

s_meters <- st_transform(slovenia_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(s_meters)

buff <- st_buffer(s_meters, dist = 1000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(slovenia_world_crop))

linestring_fix <- st_difference(buffer_outline_fixed, slovenia) ## now grab only the outline 
mapview(linestring_fix)

## make a spatiallinesdataframe so we can use sample.line
slovenia_crop <- as(linestring_fix, "Spatial")
class(slovenia_crop)
mapview(slovenia_crop)

slovenia_points_lines <- sample.line(slovenia_crop, n = 41) ## equally place the number of farms along the coastline 
class(slovenia_points_lines)
plot(slovenia_points_lines)

slovenia_points <- st_as_sf(slovenia_points_lines) %>%
  mutate(new_id = 1:41)
mapview(slovenia_points)

## Now filter out the points that fall outside of Slovenia
slovenia_points_final <- slovenia_points[2:21,]
mapview(slovenia_points_final)

mean(st_distance(slovenia_points_final, slovenia_world_crop))
# 998.6394 [m]
## close enough to 1 km

@@

croatia <- ne_countries(scale = 10, country = "Croatia", returnclass = "sf")

#info of our spatial vector object
mapview(croatia)
plot(croatia)

@@

croatia_world_crop <- st_crop(world, croatia_world_crs)

croatia_world_crop <- st_intersection(croatia_world_crop, croatia)
mapview(croatia_world_crop)
# %>% ## crop to croatia extent
#   filter(!(FID %in% c(46278:46281, 643461:643463, 156618, 46260:46269, 46178:46182, 46177, 206670:206671))) %>%
#   mutate(new_id = 1) %>%
#   group_by(new_id) %>%
#   summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
#   ungroup()
# mapview(croatia_world_crop)

c_meters <- st_transform(croatia_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(c_meters)

buff <- st_buffer(c_meters, dist = 40000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(croatia_world_crop))

linestring_fix <- st_difference(buffer_outline_fixed, croatia) ## now grab only the outline 
mapview(linestring_fix)

croatia_crop <- as(linestring_fix, "Spatial")
plot(croatia_crop)
mapview(croatia_crop)

croatia_points_lines <- sample.line(croatia_crop, n = 640) ## equally place the number of farms along the coastline 
class(croatia_points_lines)
plot(croatia_points_lines)

croatia_points <- st_as_sf(croatia_points_lines) %>%
  mutate(new_id = 1:640)
mapview(croatia_points)

## Now filter out the points that fall outside of croatia: rows 57-70
croatia_points_final <- croatia_points %>%
  dplyr::filter(new_id %in% c(2:24, 395:640)) %>%
  dplyr::filter(!(new_id %in% c(419, 533, 561)))
mapview(croatia_points_final)

mean(st_distance(croatia_points_final, croatia_world_crop))

@@

```{r}
# world <- ne_coastline(scale = 10) #world map with 10m resolution
# plot(world)

@@

#info of our spatial vector object
mapview(kerala_state)
plot(kerala_state)

# world <- st_as_sf(world)

kerala_state_world_crs <- st_transform(kerala_state, crs(coast_raw))

kerala_state_world_crop <- st_crop(coast_raw, kerala_state_world_crs) %>% ## crop to kerala extent
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
  ungroup()
mapview(kerala_state_world_crop)

k_meters <- st_transform(kerala_state_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(k_meters)

buff <- st_buffer(k_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(kerala_state_world_crop))

india <- ne_countries(scale = 10, country = "India", returnclass = "sf")
mapview(india)

linestring_fix <- st_difference(buffer_outline_fixed, india) ## now grab only the outline 
mapview(linestring_fix)
mapview(kerala_state_world_crop)
mapview(kerala_state)

kerala_state_crop <- as(linestring_fix, "Spatial")
plot(kerala_state_crop)
mapview(kerala_state_crop)

kerala_state_points_lines <- sample.line(kerala_state_crop, n = 280) ## equally place the number of farms along the coastline 
class(kerala_state_points_lines)
plot(kerala_state_points_lines)

kerala_state_points <- st_as_sf(kerala_state_points_lines) %>%
  mutate(new_id = 1:280) 
mapview(kerala_state_points)

# Now filter out the points that fall outside of kerala_state: rows 57-70
kerala_state_points_final <- kerala_state_points %>%
  filter(new_id %in% c(31:280))
mapview(kerala_state_points_final)

mean(st_distance(kerala_state_points_final, kerala_state_world_crop))

## get lat lon
ind_pts <- st_centroid(kerala_state_points_final)

@@

```{r}
# world <- ne_coastline(scale = 110) #world map with 110m resolution
# plot(world)

@@

#info of our spatial vector object
mapview(north_korea)
plot(north_korea)

# world <- st_as_sf(world)

north_korea_world_crs <- st_transform(north_korea, crs(coast_raw))

north_korea_world_crop <- st_crop(coast_raw, north_korea_world_crs) %>% ## crop to north korea extent
  dplyr::filter(!(FID %in% c(44790, 135067, 44788:44789, 135092, 135103, 87219, 44955))) %>%
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()

mapview(north_korea_world_crop)

nk_meters <- st_transform(north_korea_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(nk_meters)

buff <- st_buffer(nk_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(north_korea_world_crop))

linestring_fix <- st_difference(buffer_outline_fixed, north_korea) ## now grab only the outline 
mapview(linestring_fix)

north_korea_crop <- as(linestring_fix, "Spatial")
plot(north_korea_crop)
mapview(north_korea_crop)

north_korea_points_lines <- sample.line(north_korea_crop, n = 85) ## equally place the number of farms along the coastline 
class(north_korea_points_lines)
plot(north_korea_points_lines)

north_korea_points <- st_as_sf(north_korea_points_lines) %>%
  mutate(new_id = 1:85)
mapview(north_korea_points)

## Now filter out the points that fall outside of north_korea: rows 57-70
north_korea_points_final <- north_korea_points %>%
  filter(new_id %in% c(1:32, 46:47, 55:80 ))
mapview(north_korea_points_final)

@@

# world <- ne_coastline(scale = 110) #world map with 110m resolution
# plot(world)

# world <- st_as_sf(world)

sta_catarina_world_crs <- st_transform(sta_catarina, crs(coast_raw))

sta_catarina_world_crop <- st_crop(coast_raw, sta_catarina_world_crs) %>% ## crop to santa catarina extent
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()

mapview(sta_catarina_world_crop)

sc_meters <- st_transform(sta_catarina_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(sc_meters)

buff <- st_buffer(sc_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)
plot(buff)

linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

linestring <- st_cast(linestring, "LINESTRING")

brazil <- ne_countries(scale = 10, country = "Brazil", returnclass = "sf")
mapview(brazil)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(brazil))

linestring_fix <- st_difference(buffer_outline_fixed, brazil) ## now grab only the outline 
mapview(linestring_fix)
plot(sta_catarina_world_crop)
mapview(sta_catarina_world_crop)

sta_catarina_crop <- as(linestring_fix, "Spatial")
plot(sta_catarina_crop)
mapview(sta_catarina_crop)

sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 4) ## equally place the number of farms along the coastline 
class(sta_catarina_points_lines)
plot(sta_catarina_points_lines)

sta_catarina_points <- st_as_sf(sta_catarina_points_lines) %>%
  mutate(new_id = 1:28) %>%
  filter(new_id != 12)
mapview(sta_catarina_points)

@@

# world <- ne_coastline(scale = 50) #world map with 50m resolution
# plot(world)

@@

# world <- st_as_sf(world)

capiz_world_crs <- st_transform(capiz, crs(coast_raw))

capiz_world_crop <- st_crop(coast_raw, capiz_world_crs) %>% ## crop to extent
  dplyr::filter(!(FID %in% c(443449, 439815, 443448, 439801))) %>%
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()

mapview(capiz_world_crop)

cp_meters <- st_transform(capiz_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(cp_meters)

buff <- st_buffer(cp_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

linestring <- st_cast(linestring, "LINESTRING")

philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
mapview(philippines)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))

linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
mapview(linestring_fix)

capiz_crop <- as(linestring_fix, "Spatial")
plot(capiz_crop)
mapview(capiz_crop)

capiz_points_lines <- sample.line(capiz_crop, n = 151) ## equally place the number of farms along the coastline 
class(capiz_points_lines)
plot(capiz_points_lines)

capiz_points <- st_as_sf(capiz_points_lines) %>%
  mutate(new_id = 1:302) %>%
  filter(!(new_id %in% c(150, 146))) %>%
  dplyr::select(-new_id)
mapview(capiz_points)

# now do negros
negros <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Negros Occidental")
mapview(negros)

negros_world_crs <- st_transform(negros, crs(coast_raw))

negros_world_crop <- st_crop(coast_raw, negros_world_crs) %>%
  filter(FID %in% c(224916:224917, 224908:224912)) %>%
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()

mapview(negros_world_crop)

n_meters <- st_transform(negros_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(n_meters)

buff <- st_buffer(n_meters, dist = 5000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

linestring <- st_cast(linestring, "LINESTRING")

philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
mapview(philippines)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))

linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
mapview(linestring_fix)

negros_crop <- as(linestring_fix, "Spatial")
plot(negros_crop)
mapview(negros_crop)

@@

# now do samar 
samar <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Samar")
mapview(samar)

samar_world_crs <- st_transform(samar, crs(coast_raw))

# marabut to veriato

samar_world_crop <- st_crop(coast_raw, samar_world_crs) %>%
  filter(FID %in% c(222688:222691, 222671:222673)) %>%
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()

mapview(samar_world_crop)

sm_meters <- st_transform(samar_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(sm_meters)

buff <- st_buffer(sm_meters, dist = 3000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

linestring <- st_cast(linestring, "LINESTRING")

philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
mapview(philippines)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))

linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
mapview(linestring_fix)

samar_crop <- as(linestring_fix, "Spatial")
plot(samar_crop)
mapview(samar_crop)

samar_points_lines <- sample.line(samar_crop, n = 283) ## equally place the number of farms along the coastline 
class(samar_points_lines)
plot(samar_points_lines)

samar_points <- st_as_sf(samar_points_lines) %>%
  mutate(new_id = 1:283) %>%
  filter(!(new_id %in% c(2:13, 108:109, 98:100, 79, 74:76, 62:66, 52:53, 14:16, 95:96))) %>%
  dplyr::select(-new_id)
mapview(samar_points)
